### 2017-01-10 paper/evaluation.tex
updated columns
Updated values from table 1
updated notation
updated table
updates and pass on rq3

To evaluate the presence of parallelization settings, we considered
the \numMedLong{} subjects from the \longg{} and \medg{} groups
identified in Section~\ref{sec:rqA}. We focused on these two groups
because given that costly test suites exist, we wanted to investigate
if their maintainers are aware of parallelization settings and how
they use these settings (see Section \ref{sec:modes}).  We computed
the frequency of the parallelism modes using a two-steps approach: the
first step (discovery) automatically finds relevant build files (\ie,
\pomf{} files with parallelization settings); the second step
(inspection) consists in a manual inspection to confirm the presence
of parallelism settings in the build file and classify them according
to the parallelism level (see Section \ref{sec:modes}).
Figure \Fix{removed} describes the discovery step: we list
the paths of all build files and filter only the files that contain
any of the keywords \CodeIn{forkMode}, \CodeIn{forkCount}, or
\CodeIn{parallel}.  Notice that, for Maven projects, any of these
keywords exist in any possible parallel setting \Fix{cite surefire
doc}. Our first step is complete but is not sound since the line that
matches one of keywords may not represent part of a real setting (\eg,
comments).  We eliminate false-positives in the confirmation step.

From the \numMedLong{} subjects, the discovery step found 2853 files
and filtered 109 relevant files. Later, from the 109 relevant files,
we confirmed \Fix{M} valid settings from \Fix{X} subjects.
\Jbc{Elaborate results} Table~\ref{tab:inspection-table} summarizes
the results from the file inspection and Figure~\ref{fig:freqmodes}
shows the distribution of parallelism modes from the \Fix{M} settings.

\begin{table}[ht!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}cccc}
        \toprule
        \multirow{2}{*}{Group} & \multirow{2}{*}{\# \pomf{}} & \# \pomf{} matched & \# projects matched\\%
                               &                             &  / false-positives &       / total\\%
        \midrule%
        Long   & 1613 & 79/\Fix{z} & \Fix{X}/\numLong{}\\%
        Medium & 1240 & 30/\Fix{y} & 22/\numMed{}\\%
        \midrule%
        Total  & 2853 & 109/\Fix{z+y} & \Fix{w}/\numMedLong{}\\%
        \bottomrule%
    \end{tabular*}
    \caption{\Fix{to-be-defined}}
    \label{tab:inspection-table} 
\end{table}

>>>>

To evaluate the presence of parallelization settings (see Section
\ref{sec:modes}), we considered the \numMedLong{} subjects from the
\longg{} and \medg{} groups identified in Section~\ref{sec:rqA}. We
focused in these two groups because given that costly test suites
exist, we investigated if the maintainers are aware of parallelization
settings.

\Jbc{methodology is poorly described...}
\Fix{
We computed the frequency of the
parallelism modes using a two-steps approach: the first step
(discovery) automatically finds relevant build files (\ie, \pomf{}
files with parallelization settings); the second step (inspection)
consists in a manual inspection to confirm the presence of parallelism
settings in the build file and classify them according to the
parallelism level.  Figure \Fix{removed}
describes the discovery step: we list the paths of all build files and
filter only the files that contain any of the keywords
\CodeIn{forkMode}, \CodeIn{forkCount}, or \CodeIn{parallel}.  Notice
that, for Maven projects, any of these keywords exist in any possible
parallel setting \Fix{cite surefire doc}. Our first step is complete
but is not sound since the line that matches one of keywords may not
represent part of a real setting (\eg, comments).  We eliminate
false-positives in the confirmation step.
}

\newcommand{\pomMedLong}{2851}

\Jbc{results from table}From the \numMedLong{} subjects, we found
\pomMedLong{} \pomf{} files and selected the 109 files that matched
with any of the configuration keywords (\ie, \CodeIn{forkCount},
\CodeIn{forkMode}, and \CodeIn{parallel}).  From these 109 build
files, we eliminated six false-positives: two were names of project
modules (\eg, \emph{camel-cookbook-parallel-processing}); one was part
of a comment; three were commented configurations. The 106 build files
with valid configurations are distributed in 41 projects from our
sample.  Table~\ref{tab:inspection-table} summarizes our results.

\begin{table}[ht!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}cccc}
        \toprule
        \multirow{2}{*}{Group} & \multirow{2}{*}{\# \pomf{}} & \# \pomf{} matched & \# projects matched\\%
                               &                             &  (false-positives) &       / total\\%
        \midrule%
        Long   & 1613 & 79 (1) & 19/\numLong{}\\%
        Medium & 1238 & 30 (5) & 22/\numMed{}\\%
        \midrule%
        Total  & \pomMedLong{} & 109 (6) & 41/\numMedLong{}\\%
        \bottomrule%
    \end{tabular*}
    \caption{Presence of parallel configurations in build files from
    projects with time-consuming tests. \Fix{explain columns}}
    \label{tab:inspection-table} 
\end{table}
